---
title: Stoplight (attentional nudge) pilot results
date: "`r Sys.Date()`"
author: "fredcallaway"
output:
  rmdformats::robobook:
    code_folding: hide
    self_contained: true
---

```{r setup, include=FALSE}
source("base.r")

h = read_csv('../data/pilot_data/traffic-light-pilot4.csv') %>%
    filter(!is_practice) %>% 
    transmute(
        agent="human",
        participant_id = participant_id,
        n_option = num_options,
        n_feature = num_features,
        decision_cost = points_click_cost,
        reveal_cost = original_item_cost,
        weight_dev = weights_deviation,
        decision_cost = click_cost,
        payoff = points_action_utility,
        n_click_highlight = num_highlight_reveals,
        highlight_loss = highlight_value_check - max_highlight_value,
        weight_highlight = highlight_weight,
        highlight_value = highlight_value_check,
        nudge = factor(!is_control, levels=c(F,T), labels=c("absent", "present"))
    )


m = read_csv('../model/results/attention_sims.csv') %>% 
    filter(reveal_cost == 3) %>% 
    mutate(
        agent="model",
        participant_id = -1,
        nudge = factor(nudge, levels=c(0,1), labels=c("absent", "present")),
        model = participant_id == "model"
    )

df = bind_rows(h, m)
```

```{r}
plot_both = function(yvar) {
    df %>% 
        # group_by(agent) %>% 
        # slice_sample(n=500) %>% 
        ggplot(aes(weight_highlight, {{yvar}}, color=nudge, fill=nudge)) +
        geom_smooth(alpha=0.2) +
        stat_summary_bin(fun.data=mean_se, bins=5) +
        facet_wrap(~agent) +
        theme(
            legend.position="top", 
            axis.line = element_blank(),
            panel.border = element_rect(colour = "black", fill = NA, size=1)
        ) + scale_colour_manual(values=c(
            "darkgray",
            "dodgerblue"
        ), aesthetics=c("fill", "colour"), name="Nudge")
}

n_participant = length(unique(h$participant_id))
n_trial = df %>%
    filter(agent == "human") %>%
    with(table(participant_id)) %>% only
```

## Description

We recruited `r n_participant` participants, each of which performed `r n_trial`
trials (excluding two practice trials). On half of trials the cost to
reveal each cell in one row (one feature) was reduced from 3 clicks to 1
click. We call this the "highlighted feature". We also manipulate the weight of
the highlighted feature: for each participant, we set the weights on the 14 nudge
and 14 control trials to approximately uniformly tile the possible range (1 to 28).
The remaining two weights on each trial were sampled uniformly so that the total weight was 30.

## Number of clicks

```{r}
plot_both(n_click_highlight) + 
  labs(x="Weight of Highlighted Feature", y="Number of Reveals\nfor Highlighted Feature")
```
 
## Value of highlighted feature

```{r}
plot_both(highlight_value) + 
  labs(x="Weight of Highlighted Feature", y="Highlighted Feature Value\nof Chosen Option")
```


## Probability of maximizing

```{r}
plot_both(as.numeric(highlight_loss == 0)) + 
  labs(x="Weight of Highlighted Feature", y="Probability of Maximizing\nHighlighted Feature")
``` 
